On the minimum leaf conductance: its role in models of plant water use, and ecological and environmental controls

### 2018-07-10 manuscript.Rmd
Added Zenodo DOI

This work was made possible by the ARC Linkage Project LP140100232. RL was supported by a Marie Curie fellowship (FP7-IOF 624473). All raw data, code and a fully reproducible workflow which generates the figures, this manuscript and all analyses are available at https://www.github.com/remkoduursma/g0paper, archived at Zenodo (doi:XXX).

>>>>

This work was made possible by the ARC Linkage Project LP140100232. RL was supported by a Marie Curie fellowship (FP7-IOF 624473). All raw data, code and a fully reproducible workflow which generates the figures, this manuscript and all analyses are available at https://www.github.com/remkoduursma/g0paper, archived at Zenodo (doi:10.5281/zenodo.1308628).
